Pillar 2 - (STM) Topic Modeling

### 2019-04-02 Pillar 2 -(STM) Topic Modeling.Rmd
revert to without covariates version

# keep most recent year
#d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```

# TF-IDF
We will perform an initial (visual) exploratory analysis of our textual data using TF- IDF.

@@

###STM Corpus
We convert our DTMs into STM corpus to access to full functionality in STM package.
```{r as STM corpus, eval = TRUE}
stm_corpus <- d_cast %>% map(asSTMCorpus)
```

##Fitting STM
We will to train several models to have some flexibility in the number of topics we select. For this purpose we want to create two tibbles. One that trains on the entire data (for use), and one that we divide on training set and test set. 
###Functions
Several functions are needed to work with tibble and tidyverse functionality:
####My_stm Function
The function `my_LDA` fits an LDA model on the DTM using the previous controls.
```{r my_STM, eval= TRUE}
my_stm <- function(n_topics, corpus){

@@

stm_model <- tibble(
  #repeat each topic number twice (once for overview and once for manual)
  n_topic = rep(topic_numbers, each = 2) ) %>%

  mutate(
    #Identification information
    Origin     = rep(c("overview", "manuals"), length(topic_numbers)),         
    `Topic ID` = paste(Origin, n_topic, sep = "_"),

    #DTM
    DTM       = pmap(.l = list(Origin), .f = extract_dtm),
    doc_names = map(DTM, rownames),

    #STM Corpus
    Corpus           = pmap(.l = list(Origin), .f = extract_corpus), 
    #Documents- STM corpus
    Documents_stm     = pmap(.l=list(Corpus),    .f = extract_documents),
    #Vocab- STM corpus
    Vocab_stm         = pmap(.l=list(Corpus),    .f = extract_vocab),
    #Data- STM corpus
    Data_stm          = pmap(.l=list(Corpus),    .f = extract_data),

    #Fit Model 
    Model  = pmap(.l = list(n_topic, Corpus), .f = my_stm),

    #Evaluation
    Exclusivity        = map(Model, exclusivity),
    semantic_coherence = pmap(.l = list(Model,DTM), semanticCoherence, M = 10), #M = num. of top words per topic
    #Alretnative input to semantic_coherence = pmap(.l = list(Model, Documents_stm), semanticCoherence, M = 10),

    #
    ##Inspection

    #Beta distribution
    Beta = pmap(.l = list(Model),  .f = tidy),
    #Gamma distribution
    Gamma = pmap(.l = list(Model, DTM), .f = my_tidy_gamma), #fix this

@@

    #END MUTATE PARENTHESIS
         )

####For evaluation
```{r models in tibble}
topic_numbers <-  seq(from = 5, to = 10, by = 5) #seq(from = 5, to = 150, by = 5)

@@

#Create plots
plot_eval("manuals")
plot_eval("overview")
```

#New Documents
##Align vocabulary
```{r align vocab}
#single case: Fasos topics
d_text1 <- d_text #backup current code

fasos_docs <- d_text$catalogues%>%filter(department == "European_studies") %>%
  select(-department)

@@

```
##Fit new docs
```{r}
model <- stm_model %>% filter(`Topic ID`=="overview_10")%>%
  pull(Model)
model <- model[[1]]

# fitting:
out <- asSTMCorpus(fasos_cast)
newdocs <- alignCorpus(new=out, old.vocab = model$vocab)
fasos_theta <- fitNewDocuments(model = model, documents=newdocs$documents) #returns a course by topic matrix

@@

new_courses_theta <- fasos_theta$theta
set_names(fasos_theta$theta, old = colnames(fasos_theta$theta), new = paste0("Topic", 1:10))
new_courses_theta %>%  mutate(Topic = paste("Topic_" rownames))
```

>>>>

# keep most recent year
#d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```
###As corpus
```{r}

```
# TF-IDF
We will perform an initial (visual) exploratory analysis of our textual data using TF- IDF.

@@

```{r covariates}
#get covariates
covariates <- tribble(
  ~Origin,    ~Data,
  "catalogues", d_text$catalogues %>% distinct(`Course ID`, department),
  "manuals", d_text$manuals %>% mutate(department = "UCM") %>% distinct(`Course ID`, department)
)
```
###STM Corpus
We convert our DTMs into STM corpus to access to full functionality in STM package.
```{r as STM corpus, eval = TRUE}

stm_corpus <- d_cast %>% map(asSTMCorpus)

##Fitting STM
We will to train several models to have some flexibility in the number of topics we select. For this purpose we want to create two tibbles. One that trains on the entire data (for use), and one that we divide on training set and test set. 
###Functions
Several functions are needed to work with tibble and tidyverse functionality:
####My_stm Function
The function `my_LDA` fits an LDA model on the DTM using the previous controls.
```{r my_STM, eval= TRUE}
my_stm <- function(n_topics, corpus, data){

@@

stm_model <- tibble(
  #repeat each topic number twice (once for overview and once for manual)
  n_topic = rep(topic_numbers, each = 2) ) %>%
  mutate(
  #Identification information
  Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         
  `Topic ID` = paste(Origin, n_topic, sep = "_"),
  #DTM

  DTM       = pmap(.l = list(Origin), .f = extract_dtm),

  doc_names = map(DTM, rownames),
  #STM Corpus
  Corpus           = pmap(.l = list(Origin),   .f = extract_corpus), 
  #Documents- STM corpus
  Documents_stm     = pmap(.l=list(Corpus),    .f = extract_documents),
  #Vocab- STM corpus
  Vocab_stm         = pmap(.l=list(Corpus),    .f = extract_vocab),
  #Data- STM corpus
  Data_stm          = pmap(.l=list(Corpus),    .f = extract_data),
  #Fit Model
  Model  = pmap(.l = list(n_topic, Corpus), .f = my_stm),

  #Evaluation
  Exclusivity        = map(Model, exclusivity),

  semantic_coherence = pmap(.l = list(Model,DTM), semanticCoherence, M = 10), #M = num. of top words per topic
  #Alretnative input to semantic_coherence = pmap(.l = list(Model, Documents_stm), semanticCoherence, M = 10),

  #
  ##Inspection
  #Beta distribution
  Beta = pmap(.l = list(Model),  .f = tidy),

  #Gamma distribution
  Gamma = pmap(.l = list(Model, DTM), .f = my_tidy_gamma), #fix this

@@

)

```
####TESTING AND INSPECTING MODELS
```{r model inspection}
my_test <-  stm_model %>% filter(n_topic == 10, Origin == "manuals")
```
####For evaluation
```{r models in tibble}
topic_numbers <-  seq(from = 5, to = 10, by = 5) #seq(from = 5, to = 150, by = 5)

@@

#Create plots
plot_eval("manuals")
plot_eval("overview")
```
#Vizualization
```{r extract topic model}
select_topic_model <- function(origin, n_topic){
  model <- stm_model %>% 
    filter(Origin == origin & n_topic == n_topic) %>%
    pull(Model)

  model <- model[[1]]
  return(model)
}

test <- select_topic_model("catalogues", 10)

plot.STM(test, "perspectives", topics = c(1,5))
```
#New Documents
##Align vocabulary
```{r align vocab}
#back up current code
d_text1 <- d_text

#single case: Fasos topics
fasos_docs <- d_text$catalogues %>%
  filter(department == "European_studies") %>%
  select(-department)

@@

```
##Fit new docs
```{r}
# fitting:
out <- asSTMCorpus(fasos_cast)
newdocs <- alignCorpus(new=out, old.vocab = model$vocab)
fasos_theta <- fitNewDocuments(model = model, documents=newdocs$documents) #returns a course by topic matrix

@@

new_courses_theta <- fasos_theta$theta

set_names(fasos_theta$theta, old = colnames(fasos_theta$theta), new = paste0("Topic", 1:10))

new_courses_theta %>%  mutate(Topic = paste("Topic_", rownames))
```
#Experiment
```{r experoment}
estimateEffect(formula = 1:5 ~department, meta = test$meta)
